\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Trevor Sherrard}
\section{Contact Me}
\begin{eventlist}
\personal
    [www.trevorsherrard.com]
    {3474 Nathaniel Rochester Hall\newline Rochester, NY 14623}
    {+1 (440) 799-2705}
    {tws4129@rit.edu}
    
\end{eventlist}

\section{Summary}
I am a roboticist, and machine vision enthusiast. I am a fourth year electrical engineering student at Rochester Institute of Technology. I am currently seeking a Co-Op for Summer 2018. 

\section{Work experience}

\begin{eventlist}

\item{May 2017 -- December 2017}
     {D3 Engineering}
     {Software Engineering Co-Op}
     
Developed board support software and various device drivers for embedded advanced driver assistance systems. Prototyped various image processing piplines using OpenCV. Designed and performed various tests to verify RTOS software functionality.

\item{January 2017 -- May 2017}
     {Alstom Signaling}
     {Train Signaling Engineering Co-Op}

Responsible for writing installation and cut-over plans based off of electrical schematics for train control rooms in the Metropolitan Atlanta Rapid Transit Authority system.

\item{September 2016 -- December 2016}
	 {RIT Research Computing}
	 {Assistant Systems Administrator}
	 
Responsible for assisting in the upkeep of RIT research computing infrastructure. Helped design workflow for faculty and graduate research students using Torch, Caffe and Cuda. 

\end{eventlist}

\section{Education}

\begin{yearlist}

\item[B.S Electrical Engineering; Robotics]{2015 -- Present}
     {Rochester Institute of Technology}
     {Computer Science House}
     
\item[Community College]{2014 -- 2015}
     {Cuyahoga Community College}
     {Physics Club}
     

\end{yearlist}


\section{Robotics Projects}

\begin{yearlist}

\item{2014}
     {SortME (\href{http://www.trevorsherrard.com/html/SortME.html}{http://www.trevorsherrard.com\newline/html/SortME.html})}
     {My Computer Vision Robot Platform}
     
\item{2015}
     {RoveME (\href{http://www.trevorsherrard.com/html/RoveME.html}{http://www.trevorsherrard.com\newline/html/RoveME.html})}
     {My Large scale, built from scratch ROS robot. Built from a basic andymark differential drive robot chasis, RoveME is my personal robotics testbed.}
     
\item{2015}
	{ToolID (\href{http://www.trevorsherrard.com/html/ToolID.html}
	{http://www.trevorsherrard.com\newline/html/ToolID.html})}
	{Automatic tool identification for the computer science house woodshop. }
 

\end{yearlist}


\section{Computer Vision Projects}

\begin{yearlist}

\item{2014}
     {HAAR Training Tutorial Web Page (\href{http://www.trevorsherrard.com/html/Haar_training.html}{http://www.trevorsherrard.com/html/\newline/Haar\_training.html})}
     {A tutorial I wrote on how to train HAAR classifiers using OpenCV. It covers everything from sample preparation to training itself.}
     
\item{2015}
     {Mobile HAAR tester application (\href{http://www.trevorsherrard.com/html/ComputerVision.html}{http://www.trevorsherrard.com/html/\newline/ComputerVision.html})}
     {An application that uses the OpenCV on the android platform to test mobile classifiers on the go. It allows for downloading of classifier on the go from a URL.}
     
\item{2015}
     {CSH Augmented Reality Logo (\href{https://youtu.be/dxlEk2E-DCk}{https://youtu.be/dxlEk2E-DCk})}
     {An Augmented Reality project for the Computer Science House at RIT.}

\end{yearlist}


\section{Professional Skills}
\begin{factlist}

\item{Advanced  level}
     {C, C++, ROS, OpenCV, Robot Drive Kinematics}

\item{Intermediate level}
     {Python, Verilog, SLAM, Linux, LiDAR}

\item{Basic level}
     {Torch, Caffe, RTOS, \LaTeX}

\end{factlist}

\section{Relevant Courses}
\begin{factlist}

\item{EE Classes}{Semiconductor Devices, Digital Systems I, Digital Systems II}

\item{Robotics}{Robotics Systems, Advanced Programming, Computational Problem Solving}

\end{factlist}

\end{document}
